A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-05-04 paper.tex
Another edit to the proof section

Correctness of $\textsc{solveUnbounded}$ follows from these invariants. The
must-invariant guarantees that the environment can force the game into an error
state from $B^M$, therefore checking whether the initial state is in $B^M$ (as
in line~5) is sufficient to return \texttt{unrealisable}. The may-invariant
tells us that if $B^m[i] \equiv B^m[i+1]$ (line~6) then $Upre(B^m[i+1])
\subseteq B^m[i+1]$, i.e. there is a fixed point in the uncontrollable
predecessor. This guarantees that the controller can force the game to stay
within $B^m[i+1]$ and avoid error states indefinitely.

>>>>

Correctness of $\textsc{solveUnbounded}$ follows from these invariants. The
must-invariant guarantees that the environment can force the game into an error
state from $B^M$, therefore checking whether the initial state is in $B^M$ (as
in line~5) is sufficient to return \texttt{unrealisable}. The may-invariant
tells us that if $B^m[i] \equiv B^m[i+1]$ (line~6) then $Upre(B^m[i]) \subseteq
B^m[i]$, i.e. $B^m[i]$ overapproximates the winning states for the environment.
We know that $I \not\in B^m[k]$ due to the post-condition of
\textsc{checkBound}, and since the may-invariant tells us that $B^m$ is
monotonic then $I$ must not be in $B^m[i]$. If $I \not\in B^m[i]$ then $I$ is
not in the winning states for the environment and the controller can always win
from $I$.
